Title here

### 2016-12-12 portfolio/text/ms.Rmd
Correct methods

\noindent This approach, combined with the lack of a global intercept,
constrains the mean change in log revenue across all fishers and years to be
zero. I.e., we assume that the data are stationary after accounting for all
covariates and including an intercept that varies with strategy-year
combinations. Initial versions of the model confirmed that the global intercept
along with strategy-level intercepts would be estimated at almost exactly zero.
The estimated $\beta_{j,t}$'s represent years when people with a particular
permit set tended to do better or worse than the long-term average for that
permit set (Fig. S\ref{fig:str-yrs}). Therefore, an individual's expected
revenue (and variability) is after accounting for the general trend in revenue
for that permit set.

@@

\noindent The $\beta_{1,j}$'s represent how much a 1\% decrease in species
diversity within a strategy translates to a Y\% change in revenue. The
$\beta_{2,j}$'s represent how much a 1\% increase in species diversity within
a strategy translates to a Y\% change in revenue. These are after controlling
for changes in effort, $\beta_3$, and the interaction between changes in effort
and changes in species diversity, $\beta_4$ and $\beta_5$.

>>>>

\noindent This approach, combined with the lack of a global intercept,
constrains the mean change in log revenue across all fishers and years to be
zero. I.e., we assume that the data are stationary after accounting for all
covariates and including an intercept that varies with strategy-year
combinations. Initial versions of the model confirmed that the global intercept
along with strategy-level intercepts would be estimated at almost exactly zero.
The estimated $\beta_{j,t}$'s represent years when people with a particular
permit set tended to collectively do better or worse than the long-term average
(Fig. S\ref{fig:str-yrs}). Therefore, an individual's expected change in revenue
(and variability) is after accounting for the general trend in revenue for that
permit set.

@@

\noindent The $\beta_{1,j}$'s and $\beta_{2,j}$'s represent how much a 1\%
decrease and 1\% increase, respectively, in the ratio of species diversity from
year-to-year within a strategy translates to a given percent change in the ratio
of revenue from year-to-year. These are after controlling for changes in effort,
$\beta_3$, and the interaction between changes in effort and changes in species
diversity, $\beta_4$ and $\beta_5$.
